---
title: "Quantitative Data Management"
subtitle: "CRMW Workshop 2"
author: "Charles Lanfear"
date: "2 Feb 2023<br>Updated: `r gsub(' 0', ' ', format(Sys.Date(), format='%d %b %Y'))`"
output:
  xaringan::moon_reader:
    css: "../assets/cam-css.css"
    lib_dir: libs
    nature:
      highlightStyle: tomorrow-night-bright
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "../assets/cam_macros.js"
      titleSlideClass: ["center","top"]
---

```{r setup, purl=FALSE}
#| include: false
options(width = 68)
set.seed(7)
knitr::opts_chunk$set(eval=TRUE, echo=TRUE, message=FALSE, warning=FALSE, dev = "svg", fig.height = 4)
```


# Today

A research question: 

.text-center[
*How are different indices of deprivation related to different types of crime in London?*
]

--

Today we will:

* Create a basic project
* Load data we will need
* Prepare the data for analysis

--

Next time (barring strike) we will:

* Visualize our data
* Model our outcomes
* Diagnose and (try to) address problems


---
# Setup

1. Open RStudio

--

2. In the project menu (top right) select *New Project...*

--

3. Select *New Directory*
   * Place it wherever you want

--

4. Go to *File > New File > R Script*
   * Immediately save (*Ctrl-S* or *⌘-S*) the blank file
   * In the save menu, create a new `code` folder and save there

--

5. Using the files tab of the bottom-right panel
   * Make sure you are in your project's main directory
   * Create a new folder called `data`

--

6. Browse to this lecture on the course website
   * [clanfear.github.io/ioc_crmw/]


---
# Data Today

Save these to the `data` directory in your project

* London Crime data - 2022

   + [Direct download link (.zip)](https://clanfear.github.io/ioc_crmw/_data/dpu-crime-met-2022.zip)
   + Source: [`data.police.uk`](https://data.police.uk/data/)


* LSOA Indices of Deprivation - 2019

   + [Direct download link (.csv)](https://clanfear.github.io/ioc_crmw/_data/imd2019lsoa.csv)
   + Source: [`opendatacommunities.org`](https://opendatacommunities.org/resource?uri=http%3A%2F%2Fopendatacommunities.org%2Fdata%2Fsocietal-wellbeing%2Fimd2019%2Findices)

* LSOA Population Density - 2014

   + [Direct download link (.xlsx)](https://clanfear.github.io/ioc_crmw/land-area-population-density-lsoa11-msoa11.xlsx)
   + Source: [data.london.gov.uk](https://data.london.gov.uk/dataset/super-output-area-population-lsoa-msoa-london)

---

# Get to Work!

Our goal:

* LSOA-unit observations
* Columns for:
   * Each index of deprivation
   * Population density
   * Violence and sexual offences
   * Robbery
   * Burglary

--

Let's work on this together!


---

# Wrap-Up

### Strike Dates

```{r, echo = FALSE}
tibble::tribble(
  ~Unit,           ~ Lecturer,           ~ Strike, ~Reschedule,
  "Ethnography",   "Dr S. Doxat-Pratt" , "9 Feb",  "8 Feb (Wed)",
  "Regression",    "Chuck" ,             "16 Feb", "None",
  "Qual Coding",   "D. Przybylska" ,     "23 Feb", "24 Feb (Fri)",
  "Quant Writing", "Chuck" ,             "2 Mar",  "None",
  "Qual Writing",  "A. Rennie",          "16 Mar", "17 Mar (Fri)"
        ) |> knitr::kable()
```

